Supplemental Material for submission ``Do Objects in Real-World Images Have a Canonical Name?''

### 2019-05-21 papers/EMNLP2019/modeling.tex
--

%\paragraph{Data}
Bottom-up was trained on a $1,600$\ object names, manually curated by the authors. % (the authors manually removed names with poor a detection performance from the original set). 
They did not merge semantically similar classes, such as \textsl{person} and \textsl{guy}, which is in line with the data structure of MN. \gbt{Carina, I don't understand the following sentence}

From this set, we test on $1,254$~names (we removed the $346$\ names which are not in MN), and on $24,585$~images from MN, after filtering those whose \vg name was not in the vocabulary. 
Note that $22,304$~of the images were also part of Bottom-up's training data; below we report separate results for data in and out of the training set. 
%
%(For those cases, we would expect that evaluating the model output on our set of names per instance to yield higher detection accuracy.)
% Despite the much larger vocabulary of MN ($XX$\ name types), $346$~types are not in MN, which we removed, resulting in a final vocabulary (\mbox{MN$\cap$VG}) of 
% Similarly, we filtered out the images of MN whose \vg name was not in \mbox{MN$\cap$VG}, which resulted in $24,585$~instances (note that of those, $22,304$~images were also part of Bottom-up's training data). 
\paragraph{Evaluation Procedure}
We apply Bottom-up to each image and extract the distribution~$S$ over object labels from the final softmax layer output for the ground-truth bounding box of the target object.\footnote{We converted the scores to our vocabulary size.}

@@

%\subsection{Results \& Discussion}
\paragraph{Results and Discussion}
Table~\ref{tab:model} shows the results, and Figure~\ref{fig:ex-high-low-agreement} the names with highest softmax scores for the images in the figure.
\gbt{Proposal: in Table~\ref{tab:model} we only put the general results (not by domain), and move the by-domain part to the supp.\ material. All important points can be made at that level, and this way we gain space.}\sz{I would not do that}
% Apart from the evaluation on the full set of instances (column \textit{\mbox{All}} in Table~\ref{tab:model}), we further assess model effectiveness on the instances whose  \vg names do not match the top response in MN (\mbox{\textit{VG}$\neq$\textit{MN}}), and on those which were not part of the set of images used for training bottom-up (\mbox{$\neg$\textit{Training}}).
% The latter two sets are disjoint. 
Strikingly, the model performs worse on \vg than on the top MN response, even though the model was trained on \vg names and saw the majority of the instances during training: It has a general accuracy of $76.8$\ on MN, $68.7$\ on \vg (see condition \textit{All}), and in the subset where the top names differ (VG$\neq$MN) the difference is even bigger,\ $52.6$ vs.\ $20.7$.
We hypothesize two main reasons for this difference.
First, the top MN name may be more reliable because it is collected from multiple subjects: For instance, in the rightmost example of the first row of Figure~\ref{fig:ex-high-low-agreement}, the VG annotator chose \textit{sandwich}, but \textit{hotdog} is more appropriate and accordingly it was chosen by most subjects in MN (note however that three subjects still chose \textit{sandwich}).
Second, the model can in some cases be subject to similar kinds of visual uncertainty as humans (cf.\ Section\ \ref{ssec:variation}), like mistaking a bridge for a street in the third image in the second row of Figure~\ref{fig:ex-high-low-agreement}.
% It achieves a higher accuracy of up to\ 55\% points on instances for which MN and the VG name differ (\textsc{buildings}, VG$\neq$MN). 
% The reasons may be that MN is more general than VG for many cases (e.g.,\ the examples for \textsl{batter} in Fig.\ \ref{fig:ex-high-low-agreement}), or that MN is more reliable due to up to $36$~annotations per instance as well as to our elicitation procedure\footnote{Recall that we instructed the workers explicitly to produce object names, and did not obtain them by canonicalizing object descriptions as was done for VG.} (e.g.,\ (\textsl{sandwich,hotdog}), Fig.\ \ref{fig:ex-high-low-agreement}).

>>>>

%\paragraph{Data}
Bottom-up was trained on a $1,600$\ object names, manually curated by the authors. % (the authors manually removed names with poor a detection performance from the original set). 
They did not merge semantically similar classes, such as \textsl{person} and \textsl{guy}, which is in line with the data structure of MN. %\gbt{Carina, I don't understand the following sentence}
%
From this set, we test on $1,254$~names (we removed the $346$\ names which are not in MN), and on $24,585$~images from MN, after filtering those whose \vg name was not in the vocabulary. 
Note that $22,304$~of the images were also part of Bottom-up's training data; below we report separate results for data in and out of the training set. 
%
%(For those cases, we would expect that evaluating the model output on our set of names per instance to yield higher detection accuracy.)
% Despite the much larger vocabulary of MN ($XX$\ name types), $346$~types are not in MN, which we removed, resulting in a final vocabulary (\mbox{MN$\cap$VG}) of 
% Similarly, we filtered out the images of MN whose \vg name was not in \mbox{MN$\cap$VG}, which resulted in $24,585$~instances (note that of those, $22,304$~images were also part of Bottom-up's training data). 
\paragraph{Evaluation Procedure}
We apply Bottom-up to each image and extract the distribution~$S$ over object labels from the final softmax layer output for the ground-truth bounding box of the target object.\footnote{We converted the scores to our vocabulary size.}

@@

%\subsection{Results \& Discussion}
\paragraph{Results and Discussion}
Table~\ref{tab:model} shows the results, and Figure~\ref{fig:ex-high-low-agreement} the names with highest softmax scores for the images in the figure.
\gbt{Proposal: in Table~\ref{tab:model} we only put the general results (not by domain), and move the by-domain part to the supp.\ material. All important points can be made at that level, and this way we gain space.}\sz{I would not do that}
% Apart from the evaluation on the full set of instances (column \textit{\mbox{All}} in Table~\ref{tab:model}), we further assess model effectiveness on the instances whose  \vg names do not match the top response in MN (\mbox{\textit{VG}$\neq$\textit{MN}}), and on those which were not part of the set of images used for training bottom-up (\mbox{$\neg$\textit{Training}}).
% The latter two sets are disjoint. 
Strikingly, the model performs worse on \vg than on the top MN response, even though the model was trained on \vg names and saw the majority of the instances during training: It has a general accuracy of $76.8$\ on MN, $68.7$\ on \vg (see condition \textit{All}), and in the subset where the top names differ (VG$\neq$MN) the difference is even bigger,\ $52.6$ vs.\ $20.7$.
We hypothesize two main reasons for this difference.
First, the top MN name may be more reliable because it is collected from multiple workers: For instance, in the rightmost example of the first row of Figure~\ref{fig:ex-high-low-agreement}, the VG annotator chose \textsl{sandwich}, but \textsl{hotdog} is more appropriate and accordingly it was chosen by most subjects in MN (note however that three workers still chose \textsl{sandwich}).
Second, the model can in some cases be subject to similar kinds of visual uncertainty as humans (cf.\ Section\ \ref{ssec:variation}), like mistaking a bridge for a street in the third image in the second row of Figure~\ref{fig:ex-high-low-agreement}.
% It achieves a higher accuracy of up to\ 55\% points on instances for which MN and the VG name differ (\textsc{buildings}, VG$\neq$MN). 
% The reasons may be that MN is more general than VG for many cases (e.g.,\ the examples for \textsl{batter} in Fig.\ \ref{fig:ex-high-low-agreement}), or that MN is more reliable due to up to $36$~annotations per instance as well as to our elicitation procedure\footnote{Recall that we instructed the workers explicitly to produce object names, and did not obtain them by canonicalizing object descriptions as was done for VG.} (e.g.,\ (\textsl{sandwich,hotdog}), Fig.\ \ref{fig:ex-high-low-agreement}).
